---
title: "Task set 1"
output:
  pdf_document: default
  word_document: default
date: "2024-11-05"
---
Task set 1

```{r}
library(ggplot2)
library(dplyr)
```

(a)
```{r}
brexit_data <- read.csv("/Users/yejingyi/Downloads/brexit.csv")
str(brexit_data)
```
```{r}
leave_majority <- brexit_data %>% filter(pct_leave > pct_remain)
leave_count <- nrow(leave_majority)
print(paste("Number of districts with majority leave vote:", leave_count))
```

263 districts had a majority leave vote

```{r}
max_leave_district <- brexit_data[which.max(brexit_data$pct_leave), ]
print(max_leave_district)
```
The district with the highest leave vote percentage is Boston

```{r}
avg_leave <- mean(brexit_data$pct_leave, na.rm = TRUE)
print(paste("Average leave vote share across districts:", round(avg_leave, 2)))
```
```{r}
total_leave_votes <- sum(brexit_data$leave, na.rm = TRUE)
total_valid_votes <- sum(brexit_data$valid_votes, na.rm = TRUE)
national_leave_share <- (total_leave_votes / total_valid_votes) * 100
cat("National vote share for leave:", round(national_leave_share, 2), "%\n")
```

(b)

```{r}
ggplot(brexit_data, aes(x = pct_leave75, y = pct_leave)) +
  geom_point() +
  labs(x = "Leave Vote Share in 1975 (%)", y = "Leave Vote Share in 2016 (%)") +
  ggtitle("Leave Vote Share: 2016 vs 1975") +
  theme_minimal()
```
```{r}
model <- lm(pct_leave ~ pct_leave75, data = brexit_data)
summary(model)
```
```{r}
brexit_data_clean <- na.omit(brexit_data %>% select(pct_leave75, pct_leave))
model <- lm(pct_leave ~ pct_leave75, data = brexit_data_clean)
brexit_data_clean$residuals <- residuals(model)
ggplot(brexit_data_clean, aes(x = pct_leave75, y = pct_leave)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "blue") +
  labs(x = "Leave Vote Share in 1975 (%)", y = "Leave Vote Share in 2016 (%)") +
  ggtitle("Scatter Plot with Regression Line") +
  theme_minimal()
ggplot(brexit_data_clean, aes(x = pct_leave75, y = residuals)) +
  geom_point() +
  labs(x = "Leave Vote Share in 1975 (%)", y = "Residuals") +
  ggtitle("Residual Plot") +
  theme_minimal()
```
The reason why the residuals are scattered may because we are lacking some
important factors in the model. In this model, we only have pct_leave75 in the 
linear regression as a factor, but tehre may have  many other factors influenced
the Brexit vote in 2016.

(c)
```{r}
library(boot)

boot_fn <- function(data, index) {
  coef(lm(pct_leave ~ pct_leave75, data = data, subset = index))[2]
}

set.seed(42)
boot_results <- boot(brexit_data, boot_fn, R = 1000)
print(boot_results)

```
Because they have different ways fo calculating standard error. The OLS model
standard error is calculated based on the linear regression assumption
(independence, homoscedasticity, and normality), while bootstrap measures 
standard error by resampling,it obtain distinct datasets by repeatedly 
sampling observations from the original dataset with replacement and then 
obtain new dataset of the same size as original dataset. Bootstrap does not
rely on assumptions. 
